---
title: "Chapter 3 Excercise"
date: "7/8/2020"
output: html_document
---

```{r setup, message = F, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

### Exercise 
1. Using the `se` dataset, make a scatterplot showing visitation to all national parks in the Southeast region with color identifying individual parks.
```{r message = F}
se <- read_csv('data/se.csv')

ggplot(data = se) +
  geom_point(aes(x = year, y = visitors, color = park_name))
```

2. Change the plot so that color indicates `state`.

3. Customize by adding your own title and theme. You can also change the text sizes and angles. Try applying a 45 degree angle to the x-axis. Use your cheatsheet!
```{r}
# 2. & 3.
ggplot(data = se) +
  geom_point(aes(x = year, y = visitors, color = state)) +
  labs(x = "Year",
       y = "Visitation",
       title = "Southeast States National Park Visitation") +
  theme_light() +
  theme(legend.title = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1, size = 14))
```

4. In the code below, why isn’t the data showing up?

**The code is missing a geom to describe how the data should be plotted.**